### 2023-10-14 FirstTent.tex
datascience

\documentclass{article}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{algorithm}
\usepackage{babel}
\usepackage{booktabs}
\begin{document}
Ciao ragazzi è bello oggi il tempo.
\begin{figure}
    \centering
    \includegraphics[width=0.6\linewidth]{Images/IMG20221231200758.jpg}
    \caption{File}
    \label{fig:}
\end{figure}
\begin{equation}
\alpha + \beta + 1_2^3
\end{equation}
\begin{itemize}
\item{Scelta1}
\item{Scelta2}
\item{Scelta3}
\end{itemize}
\end{document}