### 2023-10-16 FirstTent.tex
Seconda modifica

\documentclass{article}
\usepackage{graphicx}
\begin{document}
Ciao ragazzi \`{e}
\begin{figure}
    \centering
    \includegraphics[width=0.5\linewidth]{Images/IMG20221231200758.jpg}
    \caption{File}
\end{figure}
\begin{equation}
\alpha + \beta + 1_2^3
\end{equation}
\begin{itemize}
\item{Scelta1}
\item{Scelta2}
\item{Scelta3}
\end{itemize}
\sum a_{a+1} + b^{sono sexy} * c_{yeaaaah}
\end{document}