### 2023-11-01 PROGETTORETINEURALI/PresentazioneRetiNeurali.tex
Bozza iniziale

\documentclass{article}
\title{"Reti Neurali e CHAT GPT"}
\author{Alessandro Meloni GEPID}
\date{}
\begin{document}
\maketitle
\begin{abstract}
    Questo sarà una piccolo riassunto del contenuto del paper.
\end{abstract}
\end{document}